### 2021-05-27 LaTeX-ACM/sections/paper.tex
frontrunning on arb

As we illustrate in Table~\ref{tab:front}, call markets have a unique profile of resilience against \emph{front-running attacks}~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash} that differs somewhat from continuous-time markets and automated market makers. Traders are sometimes distinguished as \emph{makers} (adds orders to a market) and \emph{takers} (trades against a pre-existing, unexecuted orders). A continuous market has both. All traders with an automated market maker are takers, while the investors who provide tokens (or liquidity) to the AMM for trading are makers. Under our definition, a call market only has makers: the only way to have a trade executed is to submit an order. The front-running attacks in Table~\ref{tab:front} are sub-categorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}. To explain the difference, we will illustrate the first three attacks in the table.

@@

Some attacks combine more than one insertion, displacement, and/or suppression attacks. AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the frontrunner's trades. In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement} and it allows traders to submit at their best price. A hybrid front-running attack allows Mallory to extract any price improvements. Consider the case where Alice's ask crosses Bob's bid with a material price improvement. Mallory inserts a bid at Alice's price, suppresses Bob's bid until the next call, and places an ask at Bob's price. She keeps buys and sells the asset and nets the price improvement as arbitrage. To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.

@@

There are two main takeaways from Table~\ref{tab:front}. Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols. A second observation is that dark call markets, like Galal \etal~\cite{}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).

@@

Arbitrum is an Ethereum Layer 2 scaling solution that operates as an optimistic roll-up~\cite{kalodner2018arbitrum}. Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or Layer 1) Ethereum DApps. To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to a Layer 1 Arbitrum contract called Inbox. The transaction is not executed, it is only recorded (as calldata) by the Inbox contract. Like any other transactions on Ethereum, miners determine the order of the transactions sent to this contract. A set of validators (open to anyone) are watching the Inbox contract for new transactions. Once an inbox transaction is finalized in an Ethereum block, validators will execute the transaction and asserts the result of the execution to other validators on a sidechain called ArbOS. Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum. As the Inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly. Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed.

@@

\textit{Testing Platforms.} Arbitrum currently operates a test network with an Inbox contract on the Ethereum Kovan testnet. To experiment with Arbitrum, we implemented a variant of \cm and ran the same experiments that we previously performed on Layer 1 (Ethereum). To call functions on \cm, traders can (i) send transactions directly to the Inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum. The sequencer will group, order,  and send all pending transactions together as a single Kovan transaction to the Inbox (and pay the gas).

@@

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus, we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Our experiments show that on Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs cost only 1,632 in Layer 1 gas (a 99.9\% savings). This is effectively the cost of recording the \texttt{closeMarket()} function call in the Inbox, which is 103 bytes of calldata. As the number of pairs increases, Layer 1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 2,656.

@@

Recall for running functions on \cm on Arbitrum, traders must first instantiate the truncation by sending it to the Arbitrum EthBridge contract. As as soon as this transaction is included in the Layer 1 (Ethereum) block, it will get time-stamped and ordered. Thus, potential for front-running on Arbitrum is same as those explained in~\ref{sec:front}.'

\textblue{Say something about \texttt{block.coinbase()} and Arbitrum.}

\textblue{Say something about sequencer.}

>>>>

As we illustrate in Table~\ref{tab:front}, call markets have a unique profile of resilience against \emph{front-running attacks}~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash} that differs somewhat from continuous-time markets and automated market makers. Traders are sometimes distinguished as \emph{makers} (adds orders to a market) and \emph{takers} (trades against a pre-existing, unexecuted orders). A continuous market has both. All traders using an automated market maker are takers, while the investors who provide tokens to the AMM (liquidity providers) are makers. Under our definition, a call market only has makers: the only way to have a trade executed is to submit an order. The front-running attacks in Table~\ref{tab:front} are sub-categorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}. To explain the difference, we will illustrate the first three attacks in the table.

@@

Some attacks combine more than one insertion, displacement, and/or suppression attacks. AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the frontrunner's trades (plus additional variants). In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement} and it allows traders to submit at their best price. A hybrid front-running attack allows Mallory to extract any price improvements. Consider the case where Alice's ask crosses Bob's bid with a material price improvement. Mallory inserts a bid at Alice's price, suppresses Bob's bid until the next call, and places an ask at Bob's price. She keeps buys and sells the asset and nets the price improvement as arbitrage. To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.

@@

There are two main takeaways from Table~\ref{tab:front}. Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols. A second observation is that dark call markets, like Galal \etal~\cite{galalpublicly}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).

@@

Arbitrum is an Ethereum Layer 2 scaling solution that operates as an optimistic roll-up~\cite{kalodner2018arbitrum}. Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or Layer 1) Ethereum DApps. To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an \textit{inbox contract} on Layer 1. The transaction is not executed, it is only recorded (as calldata) in the inbox. Like any other transactions on Ethereum, miners determine the order of the transactions sent to this contract. A set of validators (open to anyone) are watching the inbox contract for new transactions. Once an inbox transaction is finalized in an Ethereum block, validators will execute the transaction and asserts the result of the execution to other validators on a sidechain called ArbOS. Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum. As the inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly. Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed.

@@

\textit{Testing Platforms.} Arbitrum currently operates a test network with an inbox contract on the Ethereum Kovan testnet. To experiment with Arbitrum, we implemented a variant of \cm and ran the same experiments that we previously performed on Layer 1 (Ethereum). To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called a \textit{Sequencer}) provided by the Arbitrum. The sequencer will group, order, and send all pending transactions together as a single Kovan transaction to the inbox (and pay the gas).

@@

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus, we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Our experiments show that on Arbitrum, heaps are 32\% more efficient than non-Heaps for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs cost only 1,632 in Layer 1 gas (a 99.9\% savings). This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata. As the number of pairs increases, Layer 1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 2,656.

@@

In the \cm variant, traders can submit transactions to the L1 inbox contract instead of directly to the \cm DApp. This has the same front-running profile as \cm itself; only the L1 destination address is different. If a sequencer is mandatory, it acts with the same privilege as an L1 Ethereum miner in ordering the transactions it receives. Technically, sequencers are not limited to roll-ups and could be used in the context of normal L1 DApps, but they are more apparent in the context of roll-ups. A sequencer could be trusted to execute transactions in the order it receives them, outsource to a fair ordering service, or (in an tacit acknowledge of the difficulties of preventing frontrunning) auction off permission to order transactions to the highest bidder. As shown in Table~\ref{tab:front}, a sequencer is an additional frontrunning actor but does not otherwise change the kinds of attacks that are possible.

% JC: I think too minor to mention
%Finally, we note a minor technical issue. Recall that in \cm, price improvements are given to miners to prevent a hybrid frontrunning attack. As Arbitrum does not run on L1, it burns (bridged) ETH sent via \texttt{block.coinbase()}. With some effort, Arbitrium could be updated to route the payment to the L1 miner of the block that added closeMarket() to the inbox.
